Assessing reliability of an online behavioural laterality battery: a pre-registered

### 2020-07-20 online_laterality_reliability.Rmd
had to change 'select' commands to 'dplyr::select' because of conflict. Also just inverted the faces data before the AIC.

Adam J. Parker

@@

myname<-'Rhyme judge RT'
tempLR<-select(LIs[LIs$exRDT==0,],RDTlog1.Lraw,RDTlog1.Rraw,handpch)
#convert back to raw time
tempLR[,1:2]<-exp(tempLR[,1:2])
session<-1
mylim<-c(500,1500)
myg1<-makerawplot(tempLR,session,myname,mylim)

tempLR<-select(LIs[LIs$exRDT==0,],RDTlog2.Lraw,RDTlog2.Rraw,handpch)
tempLR[,1:2]<-exp(tempLR[,1:2]) #convert from log back to original scale for plot
session<-2
myg2<-makerawplot(tempLR,session,myname,mylim)

myname<-'Dichotic accuracy'
tempLR<-select(LIs[LIs$exclude<2,],DL1.Lraw,DL1.Rraw,handpch)
session<-1
mylim<-c(0,100)
myg3<-makerawplot(tempLR,session,myname,mylim)
tempLR<-select(LIs[LIs$exclude<2,],DL2.Lraw,DL2.Rraw,handpch)
session<-2
myg4<-makerawplot(tempLR,session,myname,mylim)

myname<-'Chimeric faces accuracy'
#LIs exclude of 1 or 12 indicates excluded from CF; retain exclude 0,2
tempLR<-select(LIs[LIs$exclude %in% c(0,2),],CF1.Lraw,CF1.Rraw,handpch)
session<-1
mylim<-c(0,100)
myg5<-makerawplot(tempLR,session,myname,mylim)
tempLR<-select(LIs[LIs$exclude %in% c(0,2),],CF2.Lraw,CF2.Rraw,handpch)
session<-2
myg6<-makerawplot(tempLR,session,myname,mylim)

myname<-'N finger sequences'
tempLR<-select(LIs,finger.L1,finger.R1,handpch)
session<-1
mylim<-c(50,180)
myg7<-makerawplot(tempLR,session,myname,mylim)
tempLR<-select(LIs,finger.L2,finger.R2,handpch)
session<-2
myg8<-makerawplot(tempLR,session,myname,mylim)

@@

```{r computepcorrRDT}
#revised this, as p.corr values now in allsum
RDT.short.dat<-allsum[allsum$exRDT==0,]
tempRDT <- select(RDT.short.dat,RDT1.pcorrL,RDT1.pcorrR,RDT2.pcorrL,RDT2.pcorrR)
allmeanpcorr <- mean(colMeans(tempRDT,na.rm=T))
allsdpcorr <- sd(c(tempRDT$RDT1.pcorrL,tempRDT$RDT1.pcorrR,tempRDT$RDT2.pcorrL,tempRDT$RDT2.pcorrR),na.rm=T)
```
### Significance of lateralisation on each task

@@

# create subset of data frame for analysis - I used LI_z measures, as they are on similar scale
interRR <- dplyr::select(interR, 'zlat_RDT_1', 'zlat_RDT_2', 'Day1_Dich_acc_Z',
                         'Day2_Dich_acc_Z', 'Day1_CF_acc_Z', 'Day2_CF_acc_Z','handedness')
# rename
interRR <- interRR %>% 
  rename(
    "Rhyme_1" = zlat_RDT_1,
    "Chimeric_1" = Day1_CF_acc_Z,
    "Dichotic_1" = Day1_Dich_acc_Z,
     "Rhyme_2" = zlat_RDT_2,
    "Chimeric_2" = Day2_CF_acc_Z,
    "Dichotic_2" = Day2_Dich_acc_Z
    )

@@

```{r prepareKievit,echo=FALSE, comment=FALSE, warning=FALSE}
library(lavaan)
library(tidyverse)
library(MASS)
library(qpcR)
# created handedness data
# now create subset of data frame for analysis
interRR <- dplyr::select(interR, 'zlat_RDT_1', 'zlat_RDT_2', 'Day1_Dich_acc_Z',
                         'Day2_Dich_acc_Z', 'Day1_CF_acc_Z', 'Day2_CF_acc_Z','handedness')
# rename
interRR <- interRR %>% 
  rename(
    "rhyme1" = zlat_RDT_1,
    "faces1" = Day1_CF_acc_Z,
    "dichotic1" = Day1_Dich_acc_Z,
     "rhyme2" = zlat_RDT_2,
    "faces2" = Day2_CF_acc_Z,
    "dichotic2" = Day2_Dich_acc_Z
    )

#remove cases with missing values
interRR<-na.omit(interRR)
# subset into right and left handers
left_dat <- subset(interRR, handedness== "Left")
right_dat <- subset(interRR, handedness== "Right")

>>>>

<!--- updated 20/7/20 to change 'select' to 'dplyr::select' to avoid conflicts-->
Adam J. Parker

@@

myname<-'Rhyme judge RT'
tempbit<-LIs[LIs$exRDT==0,]
tempLR<-dplyr::select(tempbit,RDTlog1.Lraw,RDTlog1.Rraw,handpch)
#convert back to raw time
tempLR[,1:2]<-exp(tempLR[,1:2])
session<-1
mylim<-c(500,1500)
myg1<-makerawplot(tempLR,session,myname,mylim)

tempLR<-dplyr::select(LIs[LIs$exRDT==0,],RDTlog2.Lraw,RDTlog2.Rraw,handpch)
tempLR[,1:2]<-exp(tempLR[,1:2]) #convert from log back to original scale for plot
session<-2
myg2<-makerawplot(tempLR,session,myname,mylim)

myname<-'Dichotic accuracy'
tempLR<-dplyr::select(LIs[LIs$exclude<2,],DL1.Lraw,DL1.Rraw,handpch)
session<-1
mylim<-c(0,100)
myg3<-makerawplot(tempLR,session,myname,mylim)
tempLR<-dplyr::select(LIs[LIs$exclude<2,],DL2.Lraw,DL2.Rraw,handpch)
session<-2
myg4<-makerawplot(tempLR,session,myname,mylim)

myname<-'Chimeric faces accuracy'
#LIs exclude of 1 or 12 indicates excluded from CF; retain exclude 0,2
tempLR<-dplyr::select(LIs[LIs$exclude %in% c(0,2),],CF1.Lraw,CF1.Rraw,handpch)
session<-1
mylim<-c(0,100)
myg5<-makerawplot(tempLR,session,myname,mylim)
tempLR<-dplyr::select(LIs[LIs$exclude %in% c(0,2),],CF2.Lraw,CF2.Rraw,handpch)
session<-2
myg6<-makerawplot(tempLR,session,myname,mylim)

myname<-'N finger sequences'
tempLR<-dplyr::select(LIs,finger.L1,finger.R1,handpch)
session<-1
mylim<-c(50,180)
myg7<-makerawplot(tempLR,session,myname,mylim)
tempLR<-dplyr::select(LIs,finger.L2,finger.R2,handpch)
session<-2
myg8<-makerawplot(tempLR,session,myname,mylim)

@@

```{r computepcorrRDT}
#revised this, as p.corr values now in allsum
RDT.short.dat<-allsum[allsum$exRDT==0,]
tempRDT <- dplyr::select(RDT.short.dat,RDT1.pcorrL,RDT1.pcorrR,RDT2.pcorrL,RDT2.pcorrR)
allmeanpcorr <- mean(colMeans(tempRDT,na.rm=T))
allsdpcorr <- sd(c(tempRDT$RDT1.pcorrL,tempRDT$RDT1.pcorrR,tempRDT$RDT2.pcorrL,tempRDT$RDT2.pcorrR),na.rm=T)
```
### Significance of lateralisation on each task

@@

# create subset of data frame for analysis - I used LI_z measures, as they are on similar scale
interRR <- dplyr::select(LIs, 'zlat_RDT_1', 'zlat_RDT_2', 'Day1_Dich_acc_Z',
                         'Day2_Dich_acc_Z', 'Day1_CF_acc_Z', 'Day2_CF_acc_Z','handedness')
# rename
interRR <- interRR %>% 
  rename(
    "Rhyme_1" = zlat_RDT_1,
    "Chimeric_1" = Day1_CF_acc_Z,
    "Dichotic_1" = Day1_Dich_acc_Z,
     "Rhyme_2" = zlat_RDT_2,
    "Chimeric_2" = Day2_CF_acc_Z,
    "Dichotic_2" = Day2_Dich_acc_Z
    )

@@

```{r prepareKievit,echo=FALSE, comment=FALSE, warning=FALSE}
library(lavaan)
library(tidyverse)
library(MASS)
library(qpcR)
# created handedness data
# now create subset of data frame for analysis
interRR <- dplyr::select(LIs, zlat_RDT_1, zlat_RDT_2, Day1_Dich_acc_Z,
                         Day2_Dich_acc_Z, Day1_CF_acc_Z, Day2_CF_acc_Z,handedness)
# rename, and reverse sign for CF
interRR <- interRR %>% 
  rename(
    "rhyme1" = zlat_RDT_1,
    "faces1" = Day1_CF_acc_Z,
    "dichotic1" = Day1_Dich_acc_Z,
     "rhyme2" = zlat_RDT_2,
    "faces2" = Day2_CF_acc_Z,
    "dichotic2" = Day2_Dich_acc_Z
    )

#remove cases with missing values
interRR<-na.omit(interRR)
interRR$faces1 <- (-interRR$faces1) #reverse sign for faces
interRR$faces2 <- (-interRR$faces2)
# subset into right and left handers
left_dat <- subset(interRR, handedness== "Left")
right_dat <- subset(interRR, handedness== "Right")
